Timely Object Recognition

### 2012-03-05 writeups/eccv12/eccv12.tex
final

\begin{abstract}
\todo{put the word visual somewhere}
In a large, multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy to decide which detector to deploy next.
The policy is guided by an estimate of the contents of the image, and is sensitive to the time deadline and the ``value'' of different classes.
We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
\end{abstract}

>>>>

\begin{abstract}
In a large visual multi-class detection system, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and that the best answer must be given by some deadline.
Our system for multi-class detection aims to give the best possible results at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic policy, guided by inference of the contents of the image, to decide which detector to deploy next.
We evaluate parametrizations of the policy with respect to performance in the novel AP vs. Time evaluation on the PASCAL VOC dataset.
\end{abstract}

### 2012-03-05 writeups/eccv12/evaluation.tex
final

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.68\linewidth]
    {figures/manual_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.68\linewidth]
    {figures/manual_plots_cls_whole.png}}
  \caption{Heuristic value function.}
  \label{fig:results_manual}
\end{figure}

@@

\todo{How do the different reward functions affect performance?}

@@

\todo{Mention how fixedorder and fastinf learn totally different weights.}

>>>>

\begin{figure}[h!]
\centering
\subfloat[Detection]{\includegraphics[width=0.78\linewidth]
    {figures/manual_plots_det_avg.png}} \\
\subfloat[Classification]{\includegraphics[width=0.78\linewidth]
    {figures/manual_plots_cls_whole.png}}
  \caption{Heuristic value function.}
  \label{fig:results_manual}
\end{figure}

@@

Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.

@@

Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights.
A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.

### 2012-03-05 writeups/eccv12/technical.tex
final

\todo{Is the above sufficiently clear?}

@@

The MRF is implemented with an open-source graphical model package \cite{Jaimovich2010}.
The parameters of the model are trained on fully-observed data.
Exact inference is generally intractable in this model.
Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \todo{cite}.

\todo{what to say about cost of inference? realistically it's 0.5 seconds while the detection action + classification is about 2 seconds.}

>>>>

@@

The MRF is implemented with an open-source graphical model package \cite{Jaimovich2010}.
The parameters of the model are trained on fully-observed data.
Exact inference is generally intractable in this model.
Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \cite{Desai2009}.
